`gosset`: An R package for analysis and synthesis of ranking data in agricultural experimentation

### 2022-06-21 inst/paper/paper.Rmd
Update paper.Rmd

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural experimentation'
abstract: null
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
header-includes: \usepackage{caption} \captionsetup[figure]{labelformat=empty}
---

@@

*Introduce the scientific background and the motivation for developing the software.*

*Explain why the software is important, and describe the exact (scientific) problem(s) it solves.*

*Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.*

*Provide a description of the experimental setting (how does the user use the software?).*

*Introduce related work in literature (cite or list algorithms used, other software etc.).*

@@

*Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.*

@@

*Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.*

@@

*Present the major functionalities of the software.*

@@

* `regret`

* `reliability`

* `worth_bar`

* `worth_map`

@@

The following lines show the first 10 rankings in the format used by the PlackettLuce package.

@@

We fit a series of Plackett-Luce models using the function `PlackettLuce` from the package of the same name as input in the lapply function.

@@

The `worth_map` function can be used to visually assess variety performance based on different traits. The values represented in a worth_map are worth estimates in log scale.

@@

***This is the main section of the article and the reviewers weight the description here appropriately***

*Indicate in what way new research questions can be pursued as a result of the software (if any).*

*Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).*

*Indicate in what way the software has changed the daily practice of its users (if so).*

*Indicate how widespread the use of the software is within and outside the intended user group.*

*Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).*

@@

*Set out the conclusion of this original software publication.*

>>>>

---
title: '`gosset`: An R package for analysis and synthesis of ranking data in agricultural experimentation'
abstract: null
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 72
bibliography: paper.bib
header-includes: \usepackage{caption} \captionsetup[figure]{labelformat=empty}
---

@@

@@

@@

@@

@@

* `regret` computes the regret [@Loomes_1982;  ].

* `reliability` computes the reliability of crop varieties, the probability to outperform the reference variety [@eskridge_1992].

* `worth_bar`  creates a bar plot of the estimated worth values for each evaluated variety.

* `worth_map` creates a heatmap plot of the estimated worth values for all varieties considering each of the
evaluated traits.

@@

The following lines show the first 10 rankings for the trait vigor, 
in the format used by the PlackettLuce package.

@@

For each trait, we fit a Plackett-Luce model using the function `PlackettLuce` from the package of the same name.
We use ``lapply`` with the list of rankings and the `PlackettLuce` function as input parameters.

@@

The `worth_map` function can be used to visually assess variety performance based on different traits. The values represented in a worth_map are worth estimates in the log scale.

@@

@@
